%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Employment}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

% %---------------------------------------------------------
%   \cventry
%     {Software Engineer} % Job title
%     {ShitOne Corp. (Start-up company)} % Organization
%     {Seoul, S.Korea} % Location
%     {Dec. 2011 - Feb. 2012} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Developed a proxy drive smartphone application which connects proxy driver and customer. Implemented overall Android application logic and wrote API server for community service, along with lead engineer who designed bidding protocol on raw socket and implemented API server for bidding.}
%       \end{cvitems}
%       \begin{cvsubentries}
%         \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
%         \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
%       \end{cvsubentries}
%     }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern on Hack Language} % Job title
    {Facebook} % Organization
    {London, UK} % Location
    {Jan 2018 - Mar 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Rearchitected Hack parser to be reactive, allowing parsing to be inlined with the computation of the result.}
        %% \item {Significantly reduced memory and garbage collection overhead. Full-codebase (hundreds of thousands of files) end-to-end parse time decreased by 25\% for the type-checker (using most of the file contents) and up to 50\% for tools that use less.}
        \item {25\% parse time reduction for the Hack type-checker (using most of the file contents) on the full-codebase.}
        \item {Up to 50\% speed up for tools that use less information(facts extraction) on hundreds of thousands of files.}
        \item {Developed a toolset to analyze and remove unnecessary build dependencies. Resulting in 2x speed up for some builds.}
      \end{cvitems}
    }
  \cventry
    {Software Engineer Intern on Developer Division} % Job title
    {Microsoft} % Organization
    {Redmond, WA} % Location
    {Jul 2017 - Oct 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engineered a new workflow to automate raw telemetry data aggregation and transformation.}
        \item {System monitors execution of user-defined query and publishes results back to data warehouse.}
        \item {Used for intermediate metrics aggregation to reduce data volumes and speed up queries.}
      \end{cvitems}
    }
  \cventry
    {Software Engineering Intern on Developer Infrastructure} % Job title
    {Google} % Organization
    {Mountain View, CA} % Location
    {Apr 2017 - Jul 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research on build/test time prediction. Performed training data analysis, model evaluation and feature engineering.}
        \item {Created tools for ML models debugging/visualization and core service efficiency evaluation.}
        \item {Helped investigating and managing incidents in complex build infrastructure at Google scale.}
      \end{cvitems}
    }
  \cventry
    {Software Engineering Intern on Developer Infrastructure} % Job title
    {Google} % Organization
    {Mountain View, CA} % Location
    {May 2016 - Aug 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engineered a service that clasterizes build targets to reduce overall resources usage.}
        \item {Performed evaluation of different batching strategies: memory, run-time optimization.}
        \item {Trained ML models to predict build memory usage and avoid out of memory errors.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
